%-------------------------
% Resume in Latex
% Author : Omkar Pote
% Based off of: https://github.com/jakegut/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\vspace*{30pt} \Huge \scshape Omkar Pote} \\ \vspace{5pt} 
    % 123 Street Name, Town, State 12345 \\ \vspace{1pt}
    \small
    \href{https://omkarpote.com}{\raisebox{-0.2\height}\faGlobe\  \underline{omkarpote.com}} ~ 
    \href{mailto:omkrpt@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{omkrpt@gmail.com}} ~
    \href{https://github.com/omkrpt}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/omkrpt}} ~ 
    \href{https://linkedin.com/in/omkrpt/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/omkrpt}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, Madras}{July 2016 -- May 2020}
      {Bachelor of Technology in Chemical Engineering}{6.25/10}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Primary Skills:}{ Java Spring Boot, RESTful services, OOP, System Design, C++, Microservices} \\
     \textbf{Languages:}{ Java, C/C++, Python, Javascript, Scala, PHP, Bash, MATLAB, LaTeX} \\
     \textbf{Big Data:}{ ETL, Spark, Databricks, AWS (EC2, EMR), Hadoop, MySQL, MongoDB, Neo4j} \\
     \textbf{Software Development:}{ OOP, SOLID principles, System Design, JUnit/Mockito, CI/CD, Agile methodologies, Git, Observability and Monitoring} \\
     \textbf{AI/ML:}{ Linear regression, Time series classification, Decision trees, Random forests, Neural networks} \\
     \textbf{Technologies/Frameworks:}{ OpenMP, Parallel programming, Docker, Kubernetes, RabbitMQ, Redis, Apache Nifi, Payment gateways, NodeJS, ReactJS, HTML/CSS} \\
    }}

 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {iACE Lab @ IIT Madras}{Oct 2023 -- Present}
      {Project Scientist}{}
      \resumeItemListStart
        \resumeItem{Working in the Intelligent Applications in Chemical Engineering
        \href{https://home.iitm.ac.in/raj/}{\underline{(iACE)}}
        Lab under Prof. Rajagopalan Srinivasan. Current research focus: XAI methods for Fault Prediction in Process Monitoring Systems.
        }
        \resumeItem{ Exploring post-hoc explainability techniques for multivariate time series classification models, to increase the reliability and trustworthiness of AI systems used by chemical plant operators with varying domain expertise and experience.
        }
    \resumeItemListEnd

    \resumeSubheading
      {HILCPS Lab @ IIT Madras}{Oct 2023 -- Present}
      {Software Quality Mentor}{}
      \resumeItemListStart
        \resumeItem{Concurrently involved with the Human-in-the-Loop Cyber-Physical Systems 
        \href{https://home.iitm.ac.in/babji.srinivasan/index.html}{\underline{(HILCPS)}}
         Lab, led by Prof. Babji Srinivasan.
        }
        \resumeItem{I oversee the project architecture and planning for an IoT project consisting of Flutter, Django, and Embedded C modules. My main responsibility here is to leverage my industry experience to guide the research group on implementing enterprise-level best practices.
        }
        \resumeItem{My current focus is to move the application to the cloud. I also assist in code review and refactoring and implement basic design patterns like Model-View-Controller.
        }
        \resumeItem{I conduct interactive sessions for the team, covering various aspects of software engineering, including agile methodologies, version control, code hygiene, and design patterns.
        }
    \resumeItemListEnd

    \resumeSubheading
      {Capillary Technologies}{May 2020 -- Sep 2023}
      {Software Developer, Payments}{Dec 2021 -- Sep 2023}
      \resumeItemListStart
        \resumeItem{
        Designed and implemented POTATO (Potato Over-The-Air Transactions Orchestrator), a robust and comprehensive solution that facilitates seamless, cashless fuel transactions at gas stations.
        }
        \resumeItem{
        Executed the entire development process, constructing the microservice architecture including a Spring Boot-based application and databases using MySQL and MongoDB.
        }
        \resumeItem{
        Built highly secure APIs for communication with Payment Service Providers, fuel stations, and third-party services.
        }
        \resumeItem{
        Continually optimized the system performance, which leverages RabbitMQ to asynchronously handle real-time transactions, accommodating a user load exceeding 10,000 per minute.
        }
        \resumeItem{
        Additionally, took charge of instituting a CI/CD pipeline and implementing real-time monitoring systems to ensure optimal functionality.
        }
      \resumeItemListEnd
\pagebreak \vspace*{30pt}

    \resumeSubSubheading
      {Big Data Engineer, Extract-Transform-Load (ETL)}{Oct 2020 -- Nov 2021}
      \resumeItemListStart
        \resumeItem{Worked on the in-house data warehousing and ETL system managing Capillary’s flagship CRM and BI product, processing over 6 billion new daily records and compiling them into a star schema-based model with facts, dimensions, and KPIs.}
        \resumeItem{ Developed REST APIs for transferring transactional and user data between internal microservices.}
        \resumeItem{Managed real-time executions, debugging, and optimizing Spark queries on AWS Elastic Map Reduce (EMR) clusters.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Intern}{May 2020 -- Sep 2020}
      \resumeItemListStart
        \resumeItem{Built internal developer tools to handle the ETL process. This includes GUIs for end-to-end control and monitoring of executions from Neo4j, where the queries are stored as a Directed Acyclic Graph.}
      \resumeItemListEnd


    \resumeSubheading
      {Tesco}{May 2019 -- Jul 2019}
      {Software Engineering Intern}{}
      \resumeItemListStart
        \resumeItem{Automated Tesco's food donation system by eliminating a labor-intensive step in stock management, optimizing processes for 2500+ stores and 6000+ charities.
        }
        \resumeItem{Developed a Donation Assistant API for product classification, implemented an Apache Nifi and Python Flask-based pipeline, reducing administrative workload by 20\%, and enhanced donation accuracy/relevance by over 15\% through data analysis using R tidyverse package.
        }
    \resumeItemListEnd

    \resumeSubheading
      {Crest IT Consulting}{Jun 2018 -- Jul 2018}
      {Web Development Intern}{}
      \resumeItemListStart
        \resumeItem{Took up a complete rebranding initiative for the company, involving the development of a new website, logo, and brand identity. Check out \href{https://crestit.in}{\underline{crestit.in}}.
        }
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Activities and Projects}
    \resumeSubHeadingListStart
        \resumeSubSubheading
            {Projects}{}
            \resumeItemListStart
                \resumeItem{\textbf{Yuj (formerly Caval):} Contributed as a founding team member for this IITM-based startup, which provided doorstep vehicle repair services. Led the development of the entire branding, logo, website, app, and other marketing materials.}
                \resumeItem{\textbf{ChemClave:} Created the ChemClave 2017 website as part of the WebOps team, for the annual event organised by the Chemical Engineering Society (CheS) of IIT Madras.}
                \resumeItem{\textbf{Cuckoo Dooku:} Developed a Star Wars-themed, open-source Chrome extension for productivity. Received a commendation in the FOSS hackathon 2021. See \href{https://github.com/omkrpt/cuckoo-dooku}{\underline{github.com/omkrpt/cuckoo-dooku}}}
                \resumeItem{\textbf{Snake Game:} Coded the game from scratch as a high school project. See
                \href{https://omkarpote.com/\#snake}{\underline{omkarpote.com/\#snake}}}
            \resumeItemListEnd
        \resumeSubSubheading
            {Graphic Design}{}
            \resumeItemListStart
                \resumeItem{\textbf{Technical Proficiency:} Skilled in graphic design using the Adobe Suite including Photoshop, Illustrator, Premiere Pro, and Indesign}
                \resumeItem{\textbf{Freelance Experience:} Freelanced for various clients from Dec'16 to Aug'18. Portfolio at 
                \href{https://www.behance.net/omkarpote}{\underline{behance.net/omkarpote}}}
                \resumeItem{\textbf{Head of Design, Entrepreneurship Cell, IIT Madras:} Led a team of 16 designers and associate designers, developing creative content for digital and printed media, over two semesters.}
                \resumeItem{\textbf{Inter IIT Sports Meet:} As part of the organizing team of the 2017 edition, designed marketing content, venue setups, and ambience for the tournament.}
            \resumeItemListEnd
        \resumeSubSubheading
            {Extracurriculars}{}
            \resumeItemListStart
                \resumeItem{\textbf{Department Soccer Team Captain:} Led the Chemical Engineering department soccer team to a third-place finish in the IITM Inter Department League 2018-19.}
                \resumeItem{\textbf{Karate:} Black belt holder with numerous accolades and medals on the national level, showcasing over 11 years of dedicated practice.}
                \resumeItem{\textbf{Music Certification:} Successfully cleared ABGMVM's Hindustani Classical Music Exam with an impressive score of 45/50.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


% \section{References}
%     \resumeItemListStart
%         \resumeItem{\textbf{Prof. Rajagopalan Srinivasan} (raj@iitm.ac.in) Professor, Chemical Engineering, IIT Madras}
%         \resumeItem{\textbf{Prof. Babji Srinivasan} (babji.srinivasan@iitm.ac.in) Associate Professor, Applied Mechanics, IIT Madras}
%     \resumeItemListEnd
        


\end{document}
